\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{listings}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{hyperref}

\title{\textbf{High Performance Computer Architectures Practical Course \\ - Exercise 4 -} \\[10mm]}
\author{Tutorium 1 \\[10mm] David Jordan (6260776) \\[1mm] Florian Rüffer (7454628) \\[1mm] Michael Samjatin (7485765) \\[10mm]}


\lstset{
    language=C++,
    basicstyle=\ttfamily,
    keywordstyle=\color{blue},
    stringstyle=\color{red},
    commentstyle=\color{green},
    numbers=left,
    numberstyle=\normalsize,
    breaklines=true,
    showstringspaces=false,
    frame=single,
    linewidth=1\linewidth,
    captionpos=b
}
\renewcommand{\lstlistingname}{File}% Listing -> Algorithm
\renewcommand{\lstlistlistingname}{List of \lstlistingname s}% List of Listings -> List of Algorithms

\begin{document}
\maketitle
\newpage
\section{Matrix}
\section{Quadratic Equation}
\section{Newton}
In this task we have to vectorize the Newton method. As mentioned in the task description
the Newton Method is an interative process to approximate the x-axis intersection. \\[5mm]

\begin{lstlisting}[caption=Newton.cpp]
    float_v FindRootVector(const float_v& p1, const float_v& p2)
    {
      float_v x = 1.f, x_new = 0.f;
      float_m mask(true);
      for( ; !mask.isEmpty(); ) {
          // for(int i = 0; i < 1000; ++i){ 
        x = x_new;
        x_new(mask) = x - F(x,p1,p2) / Fd(x,p1,p2);
        mask = abs((x_new - x)/x_new) > P;
      }
      return x_new;
    }
\end{lstlisting}

\noindent The main idea of vectorizing the Newton method, is the calculation of multiple roots at once.
This comes along with an issue, because if multiple roots are calculate, then also some of those will
reach the desired precision earlier than others. To solve this problem we will use masks.
The underlying principle of masks is a vector with each value mapped to a boolean.
Each boolean value corresponds to the value of another vector.
Using this methodology we can assign 'false' to a corresponding number, which already has our desired precision and therefore
exclude it from further unneccessary calculations.\\

\noindent The first iteration will start with a mask of only 'true' values, as no value has yet reached the desired precision.
This means every value will be updated accordingly with $x - F (x , p1 , p2 ) / Fd (x , p1 , p2 ) $.
The next iteration will only update those values, which need further refinement ($\rightarrow$ mask value equals 'true') with $mask = abs (( x_new - x ) / x_new ) > P $.

\begin{figure}[H]
    \begin{center}
        \begin{tikzpicture}[
            declare function={
                func(\x)= \x^3 - 2*\x + 2;
                derivative(\x) = 3*\x^2 - 2;
            }
        ]
        \begin{axis}[
            axis lines=middle,
            xlabel=$x$,
            ylabel={$f(x)$},
            domain=-2.5:2.5,
            samples=200,
            legend pos=outer north east
        ]
        \addplot [thick, black, smooth] {func(x)};
        \addlegendentry{$f(x)$}
        \addplot [thick, blue, smooth] {derivative(x)};
        \addlegendentry{$f'(x)$}
        
        \pgfmathsetmacro{\a}{1}
        \pgfmathsetmacro{\b}{\a - func(\a)/derivative(\a)}
        
        \addplot [green, dashed, samples=2, domain=(-2.5:2.5)] {(func(\a) + derivative(\a) * (x - \a))};
        \addlegendentry{$x_0$}
        
        \pgfmathsetmacro{\a}{\b}
        \pgfmathsetmacro{\b}{\a - func(\a)/derivative(\a)}
        
        \addplot [orange, dashed, samples=2, domain=(-2.5:2.5)] {(func(\a) + derivative(\a) * (x - \a))};
        \addlegendentry{$x_1$}
        
        \pgfmathsetmacro{\a}{\b}
        \pgfmathsetmacro{\b}{\a - func(\a)/derivative(\a)}
        
        \end{axis}
        \end{tikzpicture}
    \end{center}   
\end{figure}
\newpage
\section{Random Access}
The first part of this exercise is done by gathering the data from the input
arry to the tmp float\_v variable according to the index array. This is done
by initializing a uint\_v vector and it's corresponding indexes. If this is
done, the goal of the subtask can be achieved by running the gather function:\\
\begin{lstlisting}[caption=gathering data]
    tmp.gather(input, ind);
\end{lstlisting}
Now we want to filter the data - from the tmp variable every value larger than
0.5. Therefore we create a specific mask with the following code:
float\_m mask = tmp $>$ 0.5f;\\
With this mask, and a new initialized variable, where we want to safe the data,
we can run the "gather" function again, with adapted parameters:\\
\begin{lstlisting}[caption=gathering filtered data]
    tmp2.gather(input, ind, mask);
\end{lstlisting}
The last part of this exercise is to put the data from the tmp float\_v variable
to the ouput array, when it satisfies a given condition.
The condition is, that all values from tmp, that are smaller than 0.5, are 
put to the array "ouput" at the places given by indices.\\
We could create a new mask, but because this mask's type is identical to
the mask above (and because the solutions does it like this), we reuse the mask
(of course with adjusted filter $<$ 0.5).\\
Lastly one can just use the scatter function with the added parameters to get the
wished results to the tmp variable.
\begin{lstlisting}[caption=scattering]
    tmp.scatter(input, ind, mask);
\end{lstlisting}






\end{document}
